Mergeable Types

### 2017-02-28 paper/implementation.tex
edit

Importantly, Irmin supports user-defined three-way merge functions for
reconciling concurrent operations. While Irmin's merge functions are
defined over objects on Irmin's content-addressable heap, \name's
merge functions are defined over OCaml types. We address this
representational mismatch with the help of OCaml's PPX metaprogramming
support~\cite{ppx} to derive bi-directional transformations between
objects on OCaml and Irmin heaps. We also derive the various
serialization functions required by Irmin\footnote{
  The Since \nameMonad monad relies on Irmin for realizing the branch
  structure, it is in fact parameterized over a mergeable type that
  implements all these functions. Thus the monad is functorized over
  the mergeable type, but not polymorphic. The convenience of type
  parameter inference that polymorphism offers can however be obtained
  for module parameters using OCaml extensioms, such as Modular
  Implicits~\cite{implicits}.
}.
Synchronization between replicas is performed using Git's notion of
pushing and pulling updates from remotes~\cite{git-tp}. As a result, we reap the
benefits of efficient delta-transfer (only missing objects are transferred between
replicas), compression and end-to-end encrypted communication between
the replicas.

>>>>

Importantly, Irmin supports user-defined three-way merge functions for
reconciling concurrent operations. While Irmin's merge functions are
defined over objects on Irmin's content-addressable heap, \name's
merge functions are defined over OCaml types. We address this
representational mismatch with the help of OCaml's PPX metaprogramming
support~\cite{ppx} to derive bi-directional transformations between
objects on OCaml and Irmin heaps. We also derive the various
serialization functions required by Irmin\footnote{
  Since the \nameMonad monad relies on Irmin for realizing the branch
  structure, it is in fact parameterized over a mergeable type that
  implements all these functions. Thus the monad is functorized over
  the mergeable type, but not polymorphic. The convenience of type
  parameter inference that polymorphism offers can however be obtained
  for module parameters using OCaml extensioms, such as Modular
  Implicits~\cite{implicits}.
}.
Synchronization between replicas is performed using Git's notion of
pushing and pulling updates from remotes~\cite{git-tp}. As a result, we reap the
benefits of efficient delta-transfer (only missing objects are transferred between
replicas), compression and end-to-end encrypted communication between
the replicas.
